\section*{Preface}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Preface}

This thesis was submitted to the Norwegian University of Science and Technology (NTNU) in completion of my master's degree in Engineering and ICT, with a specialization in the field of Marine Cybernetics. The work presented herein was carried out during the spring of 2019 under the guidance of Professor Roger Skjetne at the Department of Marine Technology, and in close collaboration with Maritime Robotics AS and Arild Hepsø who has been co-supervising this thesis. This work is a continuation of the work done during my specialization project in the autumn of 2018.  

\subsection*{Acknowledgments}

A huge thanks to my supervisor, Professor Roger Skjetne, for his helpful guidance and supervision. He has supported me with his great knowledge of marine control engineering, guiding me in the right direction and providing me with good ideas on how to solve the problem.

I would also like to extend my sincere gratitude to all the people at Maritime Robotics AS that have supported me. They had the idea that inspired this thesis and have been invaluable in making the project come to life. I am in particular grateful to Arild Hepsø, Stephanie Kemna, Kenan Trnka and Sindre Fossen. They have provided me with ideas, helped solve technical difficulties, and given me valuable feedback on this report.

\vspace{1.5cm}

\centerline{Trondheim, June 10th, 2019}

\vspace{1cm}

\centerline{Jan Henrik Lenes}

\clearpage